Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences

### 2019-02-26 draft.tex

%TODO remove this before submission
	\tolerance=2000
	%Accept overfull hbox up to...
	\hfuzz=1cm
	%Reduces verbosity about the bad line breaks.
	\hbadness 10000
	%Reduces verbosity about the underful vboxes.
	\vbadness=10000

@@

The max regret $\MR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with each other alternative in $A$.
Optimal alternatives w.r.t. minimax regret are the ones with least max regret. 
Notice that, whenever the PMR of an alternative $x$ (against some other alternative) exceeds the best MR value found so far, we don't need to further evaluate $x$. 
This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2011}.

@@

\begin{table}
	\begin{center}
		\begin{tabular}{rr@{ ± }lr@{ ± }lr@{ ± }l}
			\toprule
			k & Random & sd & Two phases & sd & Pess & sd \\
			\midrule
			0 & 4.0 & 0 & 4.0 & 0 & 4.0 & 0\\
			5 & 3.40 & 0.40 & 3.86 & 0.13 & 2.63 & 0.28\\
			10 & 2.59 & 0.75 & 2.63 & 0.39 & 1.29 & 0.50\\
			15 & 2.37 & 0.33 & 0.92 & 0.76 & 0.43 & 0.50\\
			20 & 1.23 & 1.04 & 0.15 & 0.23 & 0.09 & 0.27\\
			25 & 0.90 & 0.80 & 0 & 0 & 0.25 & 0.75 \\
			30 & 0.34 & 0.57 & 0.02 & 0 & 0 & 0\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Minimax regret in problems of size $(4, 4)$ after $k$ questions.}
	\label{fig:xp1}
\end{table}

\begin{table}
	\begin{center}
		\begin{tabular}{rr@{ ± }lr@{ ± }lr@{ ± }l}
			\toprule
			k & Random & sd & Two phases & sd & Pess & sd \\
			\midrule
			0 & 5.0 & 0 & 5.0 & 0 & 5.0 & 0\\
			5 & 4.93 & 0.16 & 4.98 & 0.01 & 4.15 & 0.32\\
			10 & 4.84 & 0.22 & 4.35 & 0.28 & 3.44 & 0.46\\
			15 & 4.28 & 0.58 & 3.70 & 0.25 & 2.66 &0.54 \\
			20 & 3.85 & 0.33 & 2.67 & 0.51 & 1.62 & 0.82\\
			25 & 3.50 & 0.78 & 2.17 & 0.66 & 0.84 &  0.57\\
			30 & 2.96 & 0.80 & 1.47 & 1.10 & 0.53 & 0.70\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Minimax regret in problems of size $(5, 5)$ after $k$ questions.}
	\label{fig:xp2}
\end{table}

\begin{table}
	\begin{center}
		\begin{tabular}{rr@{ ± }lr@{ ± }lr@{ ± }l}
			\toprule
			k & Random & sd & Two phases & sd & Pess & sd \\
			\midrule
			0 & 6.0 &  &  &  &  & \\
			5 &  &  &  &  &  & \\
			10 &  &  &  &  &  & \\
			15 &  &  &  &  &  & \\
			20 &  &  &  &  &  & \\
			25 &  &  &  &  &  &  \\
			30 &  &  &  &  &  & \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Minimax regret in problems of size $(6, 6)$ after $k$ questions.}
	\label{fig:xp3}
\end{table}

We test the elicitation protocols in randomly generated datasets. %TODO and real datasets. (sushi and iris).
Our goal is to see how much we gain with an interleaved elicitation approach mixing questions to the chair and questions asked to the agents compared to performing a partial elicitation of the rule first and then eliciting the agents preferences. We also want to see how realistic our approach is for various problem sizes, by estimating the number of questions we would have to ask before being able to reduce the worst regret significantly.

>>>>

%	\tolerance=2000
%	%Accept overfull hbox up to...
%	\hfuzz=1cm
%	%Reduces verbosity about the bad line breaks.
%	\hbadness 10000
%	%Reduces verbosity about the underful vboxes.
%	\vbadness=10000

@@

The max regret $\MR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with each other alternative in $A$.
Optimal alternatives w.r.t. minimax regret are the ones with least max regret. 
Notice that, whenever the PMR of an alternative $x$ (against some other alternative) exceeds the best MR value found so far, we don't need to further evaluate $x$, as it can't be optimal. 
This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2011}.

@@

\begin{table}
	\begin{center}
		\begin{tabular}{rr@{ ± }lr@{ ± }lr@{ ± }l}
			\toprule
			k & Rnd & sd & Two ph. & sd & Pess. & sd \\
			\midrule
			0 & 4.0 & 0 & 4.0 & 0 & 4.0 & 0\\
			5 & 3.40 & 0.40 & 3.86 & 0.13 & 2.63 & 0.28\\
			10 & 2.59 & 0.75 & 2.63 & 0.39 & 1.29 & 0.50\\
			15 & 2.37 & 0.33 & 0.92 & 0.76 & 0.43 & 0.50\\
			20 & 1.23 & 1.04 & 0.15 & 0.23 & 0.09 & 0.27\\
			25 & 0.90 & 0.80 & 0 & 0 & 0.25 & 0.75 \\
			30 & 0.34 & 0.57 & 0.02 & 0 & 0 & 0\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Minimax regret in problems of size $(4, 4)$ after $k$ questions.}
	\label{fig:xp1}
\end{table}

\begin{table}
	\begin{center}
		\begin{tabular}{rr@{ ± }lr@{ ± }lr@{ ± }l}
			\toprule
			k & Rnd & sd & Two ph. & sd & Pess. & sd \\
			\midrule
			0 & 5.0 & 0 & 5.0 & 0 & 5.0 & 0\\
			5 & 4.93 & 0.16 & 4.98 & 0.01 & 4.15 & 0.32\\
			10 & 4.84 & 0.22 & 4.35 & 0.28 & 3.44 & 0.46\\
			15 & 4.28 & 0.58 & 3.70 & 0.25 & 2.66 &0.54 \\
			20 & 3.85 & 0.33 & 2.67 & 0.51 & 1.62 & 0.82\\
			25 & 3.50 & 0.78 & 2.17 & 0.66 & 0.84 &  0.57\\
			30 & 2.96 & 0.80 & 1.47 & 1.10 & 0.53 & 0.70\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Minimax regret in problems of size $(5, 5)$ after $k$ questions.}
	\label{fig:xp2}
\end{table}

\begin{table}
	\begin{center}
		\begin{tabular}{rr@{ ± }lr@{ ± }lr@{ ± }l}
			\toprule
			k & Rnd & sd & Two ph. & sd & Pess. & sd \\
			\midrule
			0 & 6.0 &  &  &  &  & \\
			5 &  &  &  &  &  & \\
			10 &  &  &  &  &  & \\
			15 &  &  &  &  &  & \\
			20 &  &  &  &  &  & \\
			25 &  &  &  &  &  &  \\
			30 &  &  &  &  &  & \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Minimax regret in problems of size $(6, 6)$ after $k$ questions.}
	\label{fig:xp3}
\end{table}

We test our strategies using randomly generated datasets. %TODO and real datasets. (sushi and iris).
Our goal is to see how much we gain with an interleaved elicitation approach mixing questions to the chair and questions asked to the agents compared to performing a partial elicitation of the rule first and then eliciting the agents preferences. We also want to see how realistic our approach is for various problem sizes, by estimating the number of questions we would have to ask before being able to reduce the worst regret significantly.
